---
title: "Through processing_node_files"
author: "Apoorb"
date: "Dec 1, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
rm(list=ls())
#2 Set Directory
#dir1="C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Through_UpStrm_Scenario_2ln/Scenarios"
dir1="/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Through_UpStrm_Scenario_2ln/Scenarios"
#dir2="C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Through_UpStrmRadar_Scenario_2ln/Scenarios"

dir=dir1
#dir=dir1
knitr::opts_knit$set(echo = TRUE,root.dir = dir)
```


#1 Loading the Libraries
```{r, results="hide"}
#********************************************************************************************************
getwd()
#********************************************************************************************************
#3 Loading Libraries
library(data.table)
library(ggplot2)
library(grid)
library(gridExtra)
#fread by default create data table. 
options(datatable.fread.datatable=TRUE)
```
#2 Reading the Node Results files   
(Node results files sometimes cotain file for base network. Delete it manually)
```{r, results="hide"}
#********************************************************************************************************
#Finidng att files 
#Find and store the files which contains length in their names
setwd(dir)

files<-list.files(pattern="_Node Results_")
#For Tesing the code logic
file<-files[[1]]
#Create empty data tables
#da contains the Average values for delay, Qlen ...
da<-data.table()
#tda contains the second by second value for delay Qlen etc .... This is used to plot
#residual queue at the start of green 
tda<-data.table()
#Loop through all the node evaluation files 
#source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/NodeFileReader.R")
source("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/NodeFileReader.R")
directory=dir
buf1<-NodeFileReader(files,dir)
da<-buf1[[1]]
tda<-buf1[[2]]

#The following code is needed if multiple runs are conducted
#This code can be used to average out the values 
da[,Qlen1:=round(mean(Qlen),digits = 2),by=list(no,dir)]
da[,veh_delay1:=round(mean(veh_delay),digits = 2),by=list(no,dir)]
da[,stop_delay1:=round(mean(stop_delay),digits = 2),by=list(no,dir)]
da[,stops1:=round(mean(stops),digits = 2),by=list(no,dir)]
da[,Qlen:=Qlen1]
da[,veh_delay:=veh_delay1]
da[,stop_delay:=stop_delay1]
da[,stops:=stops1]
da<-unique(da,by=c("no","dir"))
da<-da[,.(no,dir,stops,veh_delay,Qlen)]
fwrite(da,"avg_Q.csv")
```
#3 Read List of scenarios and Merge above data table. Plot Delay and Queue
```{r, results="hide"}
setnames(da,"no","Scenario")
if(dir==dir1){
  list_sen<-fread("List_of_senarios_Induc_60MPh_2ln.csv")

}else{
  list_sen<-fread("List_of_senarios_Radar_60MPh_2ln.csv")
}
setnames(list_sen,"S.No","Scenario")
setnames(list_sen,"EBT Vol","EBT_Vol")
setnames(list_sen,"Passage Time","Passage_time")
list_sen[,Option:=as.character(Option)]
list_sen[Option=="1",Option:="Stopbar Detector on Seperate Channel"]
list_sen[Option=="3",Option:="All Detectors on Same Channel"]

da<-merge(da,list_sen)


gap_label<-c(`0.1`="0.1 Sec Passage time",`2.5`="2.5 Sec Passage time",`5`="5 Sec Passage time")
vol_label<-c(`400`="400 veh/hr",`800`="800 veh/hr",`1200`="1200 veh/hr")
da[dir=="all",dir:="All"]
da[dir=="ebt",dir:="EBT"]
da[dir=="nbt",dir:="NBT"]


if(dir1==dir){
  det_type<-"Induction Loop Detectors"
}else{
  det_type<-"Video Detectors"
}

#source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code//GGplots_Function.R")\
source("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/GGplots_Function.R")
library(RColorBrewer)
darkcols <- brewer.pal(8, "Dark2")

a<-det_plots(data1=da,
  x1=factor(Passage_time),
  y1=veh_delay,
  fill1=factor(dir),
  facet1=EBT_Vol~Option,
  ylab1="Average Delay (veh-sec/sec)",
  title1="Average Delay"
)
a<-a+ylim(0,80)

b<-det_plots(data1=da,
  x1=factor(Passage_time),
  y1=Qlen,
  fill1=factor(dir),
  facet1=EBT_Vol~Option,
  ylab1="Average Queue Length (ft/sec)",
  title1="Average Queue Length"
)
b<-b+ylim(0,300)


```


#EBT
#4 Read all the Signal Change Files. Read the notes in Detector Project notebook to understand the format
```{r, results="hide"}
#Finidng .lsa files 
#Find and store the files which contains length in their names
files<-list.files(pattern=glob2rx("S*lsa"))
file<-files[[1]]
par(mfrow=c(2,2))
SdaEBT<-data.table()
#source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScTimingReader.R")
source("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScTimingReader.R")
SdaEBT<-scTimeRead_seed1(6,files)

```

#EBT Residual Queue
#6 Combine Signal data with queue data and Plot residual queues
```{r, results="hide"}
#**********************************************************************************************************************
#Residual Queue at start of red or end of green  
tda1<-tda
tda1[,c("st","et"):=tstrsplit(tint,"-")]
tda1[,et:=as.numeric(et)]
tda1<-tda1[,.(et,no,run_no,dir,Qlen)]
SdaEBT<-SdaEBT[Indi_cor=="amber"]
tda1<-tda1[dir=="ebt",]
EBT_residualQ<-merge(tda1,SdaEBT,by.x =c("no","run_no","et"),by.y=c("no","run_no","simS"))
EBT_residualQ<-EBT_residualQ[,.(et,Qlen,dir,no,run_no)]
EBT_residualQ<-EBT_residualQ[,AvgResQ:=mean(Qlen),by=list(no)]
EBT_residualQ<-unique(EBT_residualQ,by=c("no"))
EBT_residualQ<-merge(EBT_residualQ,list_sen,by.x="no",by.y="Scenario")

gResQ<-det_plots_2(data1=EBT_residualQ,
  x1=factor(Passage_time),
  y1=AvgResQ,
  fill1=factor(Passage_time),
  facet1=EBT_Vol~Option,
  ylab1="Average Residual Queue Length (ft/sec)",
  title1="EBT Average Residual Queues"
)
gResQ<-gResQ+ylim(0,300)
```

# NBT Residual Queue
#7 Read all the Signal Change Files. Read the notes in Detector Project notebook to understand the format
#Reading files for phase 4 (NBT)
```{r, results="hide"}
#Finidng .lsa files 
#Find and store the files which contains length in their names
files<-list.files(pattern=glob2rx("S*lsa"))
par(mfrow=c(2,2))
SdaNBT<-data.table()
#source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScTimingReader.R")
SdaNBT<-scTimeRead_seed1(4,files)
```

#NBT
#9 Combine Signal data with queue data and Plot residual queues
```{r, results="hide"}
#**********************************************************************************************************************
#**********************************************************************************************************************
#Residual Queue at start of red or end of green  
tda2<-tda
tda2[,c("st","et"):=tstrsplit(tint,"-")]
tda2[,et:=as.numeric(et)]
tda2<-tda2[,.(et,no,run_no,dir,Qlen)]
SdaNBT<-SdaNBT[Indi_cor=="amber"]
tda2<-tda2[dir=="nbt",]
NBT_residualQ<-merge(tda2,SdaNBT,by.x =c("no","run_no","et"),by.y=c("no","run_no","simS"))
NBT_residualQ<-NBT_residualQ[,.(et,Qlen,dir,no,run_no)]
NBT_residualQ<-NBT_residualQ[,AvgResQ:=mean(Qlen),by=list(no)]
NBT_residualQ<-unique(NBT_residualQ,by=c("no"))
NBT_residualQ<-merge(NBT_residualQ,list_sen,by.x="no",by.y="Scenario")

gResQ1<-det_plots_2(data1=NBT_residualQ,
  x1=factor(Passage_time),
  y1=AvgResQ,
  fill1=factor(Passage_time),
  facet1=EBT_Vol~Option,
  ylab1="Average Residual Queue Length (ft/sec)",
  title1="NBT Average Residual Queues"
)
gResQ1<-gResQ1+ylim(0,100)


```


#C Reading the SC Detector record
```{r}
#Finidng .ldp files 
#Find and store the files which contains length in their names
files<-list.files(pattern=glob2rx("*.ldp"))
file<-files[[1]]
par(mfrow=c(2,2))
SdaMax<-data.table()
#source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScDetectorRecordFileReader_HighSpeed.R")
source("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScDetectorRecordFileReader_HighSpeed.R")

store_SCL<-ScMaxOutFun_HgSpd(files,list_sen)
SdaMax<-store_SCL[[1]]
SdaMax<-SdaMax[,lapply(.SD,mean),by=list(no)]
tp<-list_sen[,.(Scenario,Option)]
SdaMax<-merge(SdaMax,tp,by.x="no",by.y="Scenario")

gmax1a<-det_plots_2(data1=SdaMax,
  x1=factor(PassageTime),
  y1=Per_EBT_MaxOout,
  fill1=factor(PassageTime),
  facet1=EBT_Vol~Option,
  ylab1="Percent Max Outs (%)",
  title1="EBT Max Outs"
)
gmax1a<-gmax1a+ylim(0,100)

gmax2a<-det_plots_2(data1=SdaMax,
  x1=factor(PassageTime),
  y1=Per_NBT_MaxOout,
  fill1=factor(PassageTime),
  facet1=EBT_Vol~Option,
  ylab1="Percent Max Outs (%)",
  title1="NBT Max Outs"
)
gmax2a<-gmax2a+ylim(0,100)

```

```{r}
MeanTime<-store_SCL[[2]]
MeanTime<-MeanTime[,lapply(.SD,mean),by=list(no)]
MeanTime<-merge(MeanTime,tp,by.x="no",by.y="Scenario")

AvgGr6<-det_plots_2(data1=MeanTime,
  x1=factor(PassageTime),
  y1=MeanGr6,
  fill1=factor(PassageTime),
  facet1=EBT_Vol~Option,
  ylab1="Average EBT Green Time (sec)",
  title1="Average EBT Green Time"
)
AvgGr6<-AvgGr6+ylim(0,80)

AvgGr4<-det_plots_2(data1=MeanTime,
  x1=factor(PassageTime),
  y1=MeanGr4,
  fill1=factor(PassageTime),
  facet1=EBT_Vol~Option,
  ylab1="Average NBT Green Time (sec)",
  title1="Average NBT Green Time"
)
AvgGr4<-AvgGr4+ylim(0,30)
```




# Graphs for no of vehicles trapped in dilemma zone
```{r}
if(dir==dir1){
#file<-"C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Through_UpStrm_Scenario_2ln/dilemma_zone.csv"
file="/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Through_UpStrm_Scenario_2ln/dilemma_zone.csv"
} else{
#file<-"C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Through_UpStrmRadar_Scenario_2ln/dilemma_zone.csv"
file="/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Through_UpStrmRadar_Scenario_2ln/dilemma_zone.csv"
}

#Create a data set to be used with dilemma zone:
dil_sig<-store_SCL[[1]][,.(no,run_no,NumEBT_Phase)]
# Graphs for no of vehicles trapped in dilemma zone
dilemma_dat<-fread(file)
dilemma_dat[,No:=.N,by=list(Scenario,Run)]
dilemma_dat<-unique(dilemma_dat,by=c("Scenario","Run"))
setnames(dilemma_dat,"No","VehDilZn")
dilemma_dat<-merge(dilemma_dat,dil_sig,by.x=c("Scenario","Run"),by.y=c("no","run_no"))
dilemma_dat[,VehDilZnPerCyc:=VehDilZn/NumEBT_Phase]
dilemma_dat[,AvgVehDilZnPerCyc:=mean(VehDilZnPerCyc),by=Scenario]
dilemma_dat<-unique(dilemma_dat,by=c("Scenario"))
dilemma_dat<-dilemma_dat[,.(Scenario,AvgVehDilZnPerCyc)]
dilemma_dat<-merge(list_sen,dilemma_dat,by="Scenario")


Grdilemma<-det_plots_2(data1=dilemma_dat,
  x1=factor(Passage_time),
  y1=AvgVehDilZnPerCyc,
  fill1=factor(Passage_time),
  facet1=EBT_Vol~Option,
  ylab1="Average Number of Vehicles Trapped in Dilemma Zone per Cycle",
  title1="Average Number of Vehicles Trapped in Dilemma Zone"
)
Grdilemma<-Grdilemma+ylim(0,3)
```




#D Saving plots in pdf for printing 
```{r}
if(dir==dir1){
  #pdf("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/results/HighSpd_Iduc.pdf")
  pdf("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/results/HighSpd_Iduc.pdf")
} else{
  #pdf("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/results/HighSpd_Radar.pdf")
  pdf("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/results/HighSpd_Radar.pdf")
}
a
b
Grdilemma
gmax1a
gmax2a
gResQ
gResQ1
AvgGr6
AvgGr4
graphics.off()

setwd("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/results")
tiff("HgSpdDelay.tiff",width=17,height=18,units = "cm",res=1000)
a
graphics.off()
tiff("HgSpdQueue.tiff",width=17,height=18,units = "cm",res=1000)
b
graphics.off()
tiff("HgSpdEBMax.tiff",width=17,height=18,units = "cm",res=1000)
gmax1a
graphics.off()
tiff("HgSpdDilZn.tiff",width=17,height=18,units = "cm",res=1000)
Grdilemma
graphics.off()
tiff("HgSpdEBRes.tiff",width=17,height=18,units = "cm",res=1000)
gResQ
graphics.off()


```


