---
title: "Through processing_node_files"
author: "Apoorb"
date: "May 31, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
rm(list=ls())
#2 Set Directory
dir1="C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Scenario_MaxGr/Scenarios"
dir1="/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Scenario_MaxGr/Scenarios"
dir=dir1
knitr::opts_knit$set(echo = TRUE,root.dir = dir)
```


#1 Loading the Libraries
```{r, results="hide"}
#********************************************************************************************************
getwd()
#********************************************************************************************************
#3 Loading Libraries
library(data.table)
library(ggplot2)
library(grid)
library(gridExtra)
#fread by default create data table. 
options(datatable.fread.datatable=TRUE)
```
#2 Reading the Node Results files   
(Node results files sometimes cotain file for base network. Delete it manually)
```{r, results="hide"}
#********************************************************************************************************
#Finidng att files 
#Find and store the files which contains length in their names
files<-list.files(pattern="_Node Results_")
#For Tesing the code logic
file<-files[[1]]
#Create empty data tables
#da contains the Average values for delay, Qlen ...
da<-data.table()
#tda contains the second by second value for delay Qlen etc .... This is used to plot
#residual queue at the start of green 
tda<-data.table()
#Loop through all the node evaluation files 
file<-files[1]

#source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/NodeFileReader.R")
source("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/NodeFileReader.R")
buf1<-NodeFileReader(files,dir)

da<-buf1[[1]]
tda<-buf1[[2]]

#The following code is needed if multiple runs are conducted
#This code can be used to average out the values 
da[,Qlen1:=round(mean(Qlen),digits = 2),by=list(no,dir)]
da[,veh_delay1:=round(mean(veh_delay),digits = 2),by=list(no,dir)]
da[,stop_delay1:=round(mean(stop_delay),digits = 2),by=list(no,dir)]
da[,stops1:=round(mean(stops),digits = 2),by=list(no,dir)]
da[,Qlen:=Qlen1]
da[,veh_delay:=veh_delay1]
da[,stop_delay:=stop_delay1]
da[,stops:=stops1]
da<-unique(da,by=c("no","dir"))
da<-da[,.(no,dir,stops,veh_delay,Qlen)]
fwrite(da,"avg_Q.csv")
```

#3 Read List of scenarios and Merge above data table. Plot Delay and Queue
```{r, results="hide"}
setnames(da,"no","Scenario")
list_sen<-fread("List_of_ScenarioMaxGr.csv")
list_sen[,MaxGrSet:=factor(MaxGrSet,levels=c("TSOH","plus5","plus10"),ordered=TRUE)]
da<-merge(da,list_sen,by.x="Scenario",by.y="S.No")
LnDist_label<-c(`50`="50-50 Lane\nDistribution",`75`="75-25 Lane\nDistribution")
gap_label<-c(`0.1`="0.1 Sec Passage time",`2.5`="2.5 Sec Passage time",`5`="5 Sec Passage time")
vol_label<-c(`400`="400 veh/hr",`800`="800 veh/hr",`1200`="1200 veh/hr")
da[dir=="all",dir:="Intersection"]
da[dir=="ebt",dir:="EBT"]
da[dir=="nbt",dir:="NBT"]



vol_label<-c(`800`="800 veh/hr",`1600`="1600 veh/hr",`2400`="2400 veh/hr")

da$EBT=da$`EBT Vol Ln1`+da$`EBT Vol Ln2`
library(RColorBrewer)
darkcols <- brewer.pal(8, "Dark2")

Vlab<-c(`800`="EBT = 800 veh/hr",`1600`="EBT = 1600 veh/hr",`2400`="EBT = 2400 veh/hr")

source("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/GGplots_Function.R")

a_comb<-TwoLndet_plots(data1=da,
             x1=factor(`Passage Time`),
             y1=veh_delay,
             fill1=factor(MaxGrSet),
             facet1=`EBT`~`Ln Dist`*dir,
             ylab1="Average Delay (veh-sec)",
             title1="Average Delay Length for Stopbar Detectors -Two Lanes",
             vol_label=Vlab
)
a_comb<-a_comb+ylim(0,55)+scale_fill_manual(name="Maximum Green\n Setting",values=darkcols[1:3])


b_comb<-TwoLndet_plots(data1=da,
             x1=factor(`Passage Time`),
             y1=Qlen,
             fill1=factor(MaxGrSet),
             facet1=`EBT`~`Ln Dist`*`dir`,
             ylab1="Average Queue Length (ft)",
             title1="Average Queue Length for Stopbar Detectors -Two Lanes",
             vol_label=Vlab
             
)
b_comb<-b_comb+ylim(0,1200)+scale_fill_manual(name="Maximum Green\n Setting",values=darkcols[1:3])
```

#C Reading the SC Detector record
```{r}
#Finidng .ldp files 
#Find and store the files which contains length in their names
files<-list.files(pattern=glob2rx("*.ldp"))
file<-files[[1]]
par(mfrow=c(2,2))
SdaMax<-data.table()
listSen<-list_sen
setnames(listSen,"S.No","Scenario")
listSen[,EBT:=`EBT Vol Ln1`+`EBT Vol Ln2`]
#source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScDetectorRecordFileReader.R")
source("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScDetectorRecordFileReader.R")

store_SCL<-ScMaxOutFun(files,listSen)

SdaMax<-store_SCL[[1]]
SdaMax<-SdaMax[,lapply(.SD,mean),by=list(no)]

SdaMax<-merge(list_sen,SdaMax,by.x="Scenario",by.y="no")
  
gmax_a_comb<-TwoLndet_plots_2(data1=SdaMax,
                    x1=factor(`Passage Time`),
                    y1=Per_EBT_MaxOout,
                    fill1=MaxGrSet,
                    facet1=`EBT`~`Ln Dist`,
                    ylab1="Percent Max Outs (%)",
                    title1="EBT Max Outs",
                    vol_label=Vlab
)
gmax_a_comb<-gmax_a_comb+ylim(0,100)+scale_fill_manual(name="Maximum Green\n Setting",values=darkcols[1:3])

gmax_b_comb<-TwoLndet_plots_2(data1=SdaMax,
                    x1=factor(`Passage Time`),
                    y1=Per_NBT_MaxOout,
                    fill1=MaxGrSet,
                    facet1=`EBT`~`Ln Dist`,
                    ylab1="Percent Max Outs (%)",
                    title1="NBT Max Outs",
                    vol_label=Vlab
)
gmax_b_comb<-gmax_b_comb+ylim(0,100)+ylim(0,100)+scale_fill_manual(name="Maximum Green\n Setting",values=darkcols[1:3])
```

```{r}
MeanTime<-store_SCL[[2]]
MeanTime<-MeanTime[,lapply(.SD,mean),by=list(no)]
MeanTime<-merge(list_sen,MeanTime,by.x="Scenario",by.y="no")


AvgGr6<-ggplot(MeanTime,aes(x=as.factor(PassageTime),y=MeanGr6,fill=as.factor(MaxGrSet)))+geom_bar(stat="Identity",color="black",position=position_dodge())+facet_grid(EBT~`Ln Dist`,labeller=labeller(EBT=vol_label,`Ln Dist`=LnDist_label))+ggtitle("Average EBT Green Time")+xlab("EBT Passage Time (sec)")+ylab("Average EBT Green Time (sec)")+theme_bw()+scale_fill_manual("Maximum Green\n Setting",values=darkcols[1:3])+ylim(0,100)+theme(axis.text.x = element_text(angle=45,hjust=1))

AvgGr4<-ggplot(MeanTime,aes(x=as.factor(PassageTime),y=MeanGr4,fill=as.factor(MaxGrSet)))+geom_bar(stat="Identity",color="black",position=position_dodge())+facet_grid(EBT~`Ln Dist`,labeller=labeller(EBT=vol_label,`Ln Dist`=LnDist_label))+ggtitle("Average NBT Green Time")+xlab("EBT Passage Time (sec)")+ylab("Average NBT Green Time (sec)")+theme_bw()+scale_fill_manual("Maximum Green\n Setting",values=darkcols[1:3])+ylim(0,80)+theme(axis.text.x = element_text(angle=45,hjust=1))
```

#EBT Residual Queue
#6 Combine Signal data with queue data and Plot residual queues
```{r, results="hide"}
#Finidng .lsa files 
#Find and store the files which contains length in their names
files<-list.files(pattern=glob2rx("S*lsa"))
file<-files[[1]]
par(mfrow=c(2,2))
SdaEBT<-data.table()
#source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScTimingReader.R")
source("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScTimingReader.R")

SdaEBT<-scTimeRead_seed1(6,files)
#**********************************************************************************************************************
#Residual Queue at start of red or end of green  
tda1<-tda
tda1[,c("st","et"):=tstrsplit(tint,"-")]
tda1[,et:=as.numeric(et)]
tda1<-tda1[,.(et,no,run_no,dir,Qlen)]
SdaEBT<-SdaEBT[Indi_cor=="amber"]
tda1<-tda1[dir=="ebt",]
EBT_residualQ<-merge(tda1,SdaEBT,by.x =c("no","run_no","et"),by.y=c("no","run_no","simS"))
EBT_residualQ<-EBT_residualQ[,.(et,Qlen,dir,no,run_no)]
EBT_residualQ<-EBT_residualQ[,AvgResQ:=mean(Qlen),by=list(no)]
EBT_residualQ<-unique(EBT_residualQ,by=c("no"))
EBT_residualQ<-merge(EBT_residualQ,list_sen,by.x="no",by.y="Scenario")

gResQ_EB<-TwoLndet_plots_2(data1=EBT_residualQ,
                    x1=factor(`Passage Time`),
                    y1=AvgResQ,
                    fill1=MaxGrSet,
                    facet1=`EBT`~`Ln Dist`,
                    ylab1="Average Residual Queues (ft)",
                    title1="2 Lanes Avg Res Q",
                    vol_label=Vlab
)
gResQ_EB<-gResQ_EB+ylim(0,2000)+scale_fill_manual("Maximum Green\n Setting",values=darkcols[1:3])
```

# NBT Residual Queue
#7 Read all the Signal Change Files. Read the notes in Detector Project notebook to understand the format
#Reading files for phase 4 (NBT)
#9 Combine Signal data with queue data and Plot residual queues
```{r, results="hide"}
#Finidng .lsa files 
#Find and store the files which contains length in their names
files<-list.files(pattern=glob2rx("S*lsa"))
par(mfrow=c(2,2))
SdaNBT<-data.table()
#source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScTimingReader.R")
source("/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScTimingReader.R")

SdaNBT<-scTimeRead_seed1(4,files)
#**********************************************************************************************************************
#**********************************************************************************************************************
#Residual Queue at start of red or end of green  
tda2<-tda
tda2[,c("st","et"):=tstrsplit(tint,"-")]
tda2[,et:=as.numeric(et)]
tda2<-tda2[,.(et,no,run_no,dir,Qlen)]
SdaNBT<-SdaNBT[Indi_cor=="amber"]
tda2<-tda2[dir=="nbt",]
NBT_residualQ<-merge(tda2,SdaNBT,by.x =c("no","run_no","et"),by.y=c("no","run_no","simS"))
NBT_residualQ<-NBT_residualQ[,.(et,Qlen,dir,no,run_no)]
NBT_residualQ<-NBT_residualQ[,AvgResQ:=mean(Qlen),by=list(no)]
NBT_residualQ<-unique(NBT_residualQ,by=c("no"))
NBT_residualQ<-merge(NBT_residualQ,list_sen,by.x="no",by.y="Scenario")

gResQ_NB<-TwoLndet_plots_2(data1=NBT_residualQ,
                    x1=factor(`Passage Time`),
                    y1=AvgResQ,
                    fill1=MaxGrSet,
                    facet1=`EBT`~`Ln Dist`,
                    ylab1="Average Residual Queues (ft)",
                    title1="2 Lanes Avg Res Q",
                    vol_label=Vlab
)
gResQ_NB<-gResQ_NB+ylim(0,2000)+scale_fill_manual("Maximum Green\n Setting",values=darkcols[1:3])
```


#D Saving plots in pdf for printing 
```{r}
mainDir<-"/Users/Apoorb/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/results"
subDir<-"MaxGrres"
dir.create(file.path(mainDir, subDir))
tem<-file.path(mainDir, subDir)


jpeg(file.path(tem,"MaxGrAvgGr4.jpeg"),width=17,height=12,units = "cm",res=1000)
AvgGr4
graphics.off()

jpeg(file.path(tem,"MaxGrAvgGr6.jpeg"),width=17,height=12,units = "cm",res=1000)
AvgGr6
graphics.off()

jpeg(file.path(tem,"MaxGrDelay.jpeg"),width=17,height=12,units = "cm",res=1000)
a_comb
graphics.off()
jpeg(file.path(tem,"MaxGrQue.jpeg"),width=17,height=12,units = "cm",res=1000)
b_comb
graphics.off()
jpeg(file.path(tem,"MaxGrEBMax.jpeg"),width=14,height=12,units = "cm",res=1000)
gmax_a_comb
graphics.off()
jpeg(file.path(tem,"MaxGrNBMax.jpeg"),width=14,height=12,units = "cm",res=500)
gmax_b_comb
graphics.off()
jpeg(file.path(tem,"MaxGrEBRes.jpeg"),width=14,height=12,units = "cm",res=500)
gResQ_EB
graphics.off()
jpeg(file.path(tem,"MaxGrNBRes.jpeg"),width=14,height=12,units = "cm",res=500)
gResQ_NB
graphics.off()

pdf(file.path(tem,"MaxGrPlt RandSeed 10-15.pdf"),width=17,height=12)
AvgGr6
AvgGr4
a_comb
b_comb
gmax_a_comb
gmax_b_comb
gResQ_EB
gResQ_NB
dev.off()
```


```{r}

```

