---
title: "Through processing_node_files"
author: "Apoorb"
date: "May 31, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
rm(list=ls())
#2 Set Directory
dir1="C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Through_STbar_Scenario/Scenarios"
dir2="C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Through_STbar_Video/Scenarios"
dir=dir2
#dir=dir1
knitr::opts_knit$set(echo = TRUE,root.dir = dir)
```


#1 Loading the Libraries
```{r, results="hide"}
#********************************************************************************************************
getwd()
#********************************************************************************************************
#3 Loading Libraries
library(data.table)
library(ggplot2)
library(grid)
library(gridExtra)
#fread by default create data table. 
options(datatable.fread.datatable=TRUE)
```
#2 Reading the Node Results files   
(Node results files sometimes cotain file for base network. Delete it manually)
```{r, results="hide"}
#********************************************************************************************************
#Finidng att files 
#Find and store the files which contains length in their names
setwd(dir)

files<-list.files(pattern="_Node Results_")
#For Tesing the code logic
file<-files[[1]]
#Create empty data tables
#da contains the Average values for delay, Qlen ...
da<-data.table()
#tda contains the second by second value for delay Qlen etc .... This is used to plot
#residual queue at the start of green 
tda<-data.table()
#Loop through all the node evaluation files 
source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/NodeFileReader.R")
directory=dir
buf1<-NodeFileReader(files,dir)
da<-buf1[[1]]
tda<-buf1[[2]]

#The following code is needed if multiple runs are conducted
#This code can be used to average out the values 
da[,Qlen1:=round(mean(Qlen),digits = 2),by=list(no,dir)]
da[,veh_delay1:=round(mean(veh_delay),digits = 2),by=list(no,dir)]
da[,stop_delay1:=round(mean(stop_delay),digits = 2),by=list(no,dir)]
da[,stops1:=round(mean(stops),digits = 2),by=list(no,dir)]
da[,Qlen:=Qlen1]
da[,veh_delay:=veh_delay1]
da[,stop_delay:=stop_delay1]
da[,stops:=stops1]
da<-unique(da,by=c("no","dir"))
da<-da[,.(no,dir,stops,veh_delay,Qlen)]
fwrite(da,"avg_Q.csv")
```
#3 Read List of scenarios and Merge above data table. Plot Delay and Queue
```{r, results="hide"}
setnames(da,"no","Scenario")
list_sen<-fread("Scenario_Through_STbar.csv")
da<-merge(da,list_sen)


gap_label<-c(`0.1`="0.1 Sec Passage time",`2.5`="2.5 Sec Passage time",`5`="5 Sec Passage time")
vol_label<-c(`400`="400 veh/hr",`800`="800 veh/hr",`1200`="1200 veh/hr")
da[dir=="all",dir:="All"]
da[dir=="ebt",dir:="EBT"]
da[dir=="nbt",dir:="NBT-60ft Det"]


if(dir1==dir){
  det_type<-"Induction Loop Detectors"
}else{
  det_type<-"Video Detectors"
}

library(RColorBrewer)
darkcols <- brewer.pal(8, "Dark2")
a<-ggplot(da,aes(x=factor(Passage_time),y=veh_delay,fill=as.factor(dir)))+geom_bar(stat="Identity",colour="black",position=position_dodge())+facet_grid(EBT_Vol~.,labeller=labeller(EBT_Vol=vol_label))+scale_fill_manual(name="Direction",values=darkcols[1:3])+labs(title=paste("Average Delay",det_type,sep=" "),x="Passage Time (sec)",y="Average Delay (veh-sec/sec)")+ theme_bw()+theme(axis.text.x = element_text(angle=45,hjust=1))+ylim(0,80)

b<-ggplot(da,aes(x=factor(Passage_time),y=Qlen,fill=as.factor(dir)))+geom_bar(stat="Identity",colour="black",position=position_dodge())+facet_grid(EBT_Vol~.,labeller=labeller(EBT_Vol=vol_label))+scale_fill_manual(name="Direction",values=darkcols[1:3])+labs(title=paste("Average Queue Length",det_type,sep=" "),x="Passage Time (sec)",y="Average Queue Length (ft/sec)")+ theme_bw()+theme(axis.text.x = element_text(angle=45,hjust=1))+ylim(0,1200)

```


#EBT
#4 Read all the Signal Change Files. Read the notes in Detector Project notebook to understand the format
```{r, results="hide"}
#Finidng .lsa files 
#Find and store the files which contains length in their names
files<-list.files(pattern=glob2rx("S*lsa"))
file<-files[[1]]
par(mfrow=c(2,2))
SdaEBT<-data.table()
source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScTimingReader.R")
SdaEBT<-scTimeRead_seed1(6,files)

```

#EBT Residual Queue
#6 Combine Signal data with queue data and Plot residual queues
```{r, results="hide"}
#**********************************************************************************************************************
#Residual Queue at start of red or end of green  
tda1<-tda
tda1[,c("st","et"):=tstrsplit(tint,"-")]
tda1[,et:=as.numeric(et)]
tda1<-tda1[,.(et,no,run_no,dir,Qlen)]
SdaEBT<-SdaEBT[Indi_cor=="amber"]
tda1<-tda1[dir=="ebt",]
EBT_residualQ<-merge(tda1,SdaEBT,by.x =c("no","run_no","et"),by.y=c("no","run_no","simS"))
EBT_residualQ<-EBT_residualQ[,.(et,Qlen,dir,no,run_no)]
EBT_residualQ<-EBT_residualQ[,AvgResQ:=mean(Qlen),by=list(no)]
EBT_residualQ<-unique(EBT_residualQ,by=c("no"))
EBT_residualQ<-merge(EBT_residualQ,list_sen,by.x="no",by.y="Scenario")

gResQ<-ggplot(EBT_residualQ,aes(x=as.factor(Passage_time),y=AvgResQ,fill=as.factor(Passage_time)))+geom_bar(stat="Identity",color="black",position=position_dodge())+facet_grid(EBT_Vol~.,labeller=labeller(EBT_Vol=vol_label))+ggtitle(paste("EBT Average Residual Queues",det_type,sep=" "))+xlab("EBT Passage Time (sec)")+ylab("Average Residual Queues (ft/sec)")+theme_bw()+scale_fill_manual(name="EBT Passage Time (sec)",values=darkcols[1:8])+ylim(0,1200)

```




# NBT Residual Queue
#7 Read all the Signal Change Files. Read the notes in Detector Project notebook to understand the format
#Reading files for phase 4 (NBT)
```{r, results="hide"}
#Finidng .lsa files 
#Find and store the files which contains length in their names
files<-list.files(pattern=glob2rx("S*lsa"))
par(mfrow=c(2,2))
SdaNBT<-data.table()
source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScTimingReader.R")
SdaNBT<-scTimeRead_seed1(4,files)
```

#NBT
#9 Combine Signal data with queue data and Plot residual queues
```{r, results="hide"}
#**********************************************************************************************************************
#**********************************************************************************************************************
#Residual Queue at start of red or end of green  
tda2<-tda
tda2[,c("st","et"):=tstrsplit(tint,"-")]
tda2[,et:=as.numeric(et)]
tda2<-tda2[,.(et,no,run_no,dir,Qlen)]
SdaNBT<-SdaNBT[Indi_cor=="amber"]
tda2<-tda2[dir=="nbt",]
NBT_residualQ<-merge(tda2,SdaNBT,by.x =c("no","run_no","et"),by.y=c("no","run_no","simS"))
NBT_residualQ<-NBT_residualQ[,.(et,Qlen,dir,no,run_no)]
NBT_residualQ<-NBT_residualQ[,AvgResQ:=mean(Qlen),by=list(no)]
NBT_residualQ<-unique(NBT_residualQ,by=c("no"))
NBT_residualQ<-merge(NBT_residualQ,list_sen,by.x="no",by.y="Scenario")

gResQ1<-ggplot(NBT_residualQ,aes(x=as.factor(Passage_time),y=AvgResQ,fill=as.factor(Passage_time)))+geom_bar(stat="Identity",color="black",position=position_dodge())+facet_grid(EBT_Vol~.,labeller=labeller(EBT_Vol=vol_label))+ggtitle(paste("NBT Average Residual Queues",det_type,sep=" "))+xlab("EBT Passage Time (sec)")+ylab("Average Residual Queues (ft/sec)")+theme_bw()+scale_fill_manual(name="EBT Passage Time (sec)",values=darkcols[1:8])+ylim(0,1200)

```


#C Reading the SC Detector record
```{r}
#Finidng .ldp files 
#Find and store the files which contains length in their names
files<-list.files(pattern=glob2rx("*.ldp"))
file<-files[[1]]
par(mfrow=c(2,2))
listSen<-fread("Scenario_Through_STbar.csv")
SdaMax<-data.table()
source("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/ScDetectorRecordFileReader.R")
store_SCL<-ScMaxOutFun(files,listSen)
SdaMax<-store_SCL[[1]]
SdaMax<-SdaMax[,lapply(.SD,mean),by=list(no)]


gmax1a<-ggplot(SdaMax,aes(x=as.factor(PassageTime),y=Per_EBT_MaxOout,fill=as.factor(PassageTime)))+geom_bar(stat="Identity",color="black",position=position_dodge())+facet_grid(EBT_Vol~.,labeller=labeller(EBT_Vol=vol_label))+ggtitle(paste("EBT Max Outs",det_type,sep=" "))+xlab("EBT Passage Time (sec)")+ylab("Percent Max Outs (%)")+theme_bw()+scale_fill_manual(name="EBT Passage Time (sec)",values=darkcols[1:8])+ylim(0,100)

gmax2a<-ggplot(SdaMax,aes(x=as.factor(PassageTime),y=Per_NBT_MaxOout,fill=as.factor(PassageTime)))+geom_bar(stat="Identity",color="black",position=position_dodge())+facet_grid(EBT_Vol~.,labeller=labeller(EBT_Vol=vol_label))+ggtitle(paste("NBT Max Outs",det_type,sep=" "))+xlab("EBT Passage Time (sec)")+ylab("Percent Max Outs (%)")+theme_bw()+scale_fill_manual(name="EBT Passage Time (sec)",values=darkcols[1:8])+ylim(0,100)
```

```{r}
MeanTime<-store_SCL[[2]]
MeanTime<-MeanTime[,lapply(.SD,mean),by=list(no)]


AvgGr6<-ggplot(MeanTime,aes(x=as.factor(PassageTime),y=MeanGr6,fill=as.factor(PassageTime)))+geom_bar(stat="Identity",color="black",position=position_dodge())+facet_grid(EBT_Vol~.,labeller=labeller(EBT_Vol=vol_label))+ggtitle(paste("Average EBT Green Time",det_type,sep=" "))+xlab("EBT Passage Time (sec)")+ylab("Average EBT Green Time (sec)")+theme_bw()+scale_fill_manual(name="EBT Passage Time (sec)",values=darkcols[1:8])+ylim(0,80)

AvgGr4<-ggplot(MeanTime,aes(x=as.factor(PassageTime),y=MeanGr4,fill=as.factor(PassageTime)))+geom_bar(stat="Identity",color="black",position=position_dodge())+facet_grid(EBT_Vol~.,labeller=labeller(EBT_Vol=vol_label))+ggtitle(paste("Average NBT Green Time",det_type,sep=" "))+xlab("EBT Passage Time (sec)")+ylab("Average NBT Green Time (sec)")+theme_bw()+scale_fill_manual(name="EBT Passage Time (sec)",values=darkcols[1:8])+ylim(0,80)
```



#D Saving plots in pdf for printing 
```{r}
if(dir==dir1){
  pdf("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/Through_InducLp_STbar.pdf")
} else{
    pdf("C:/Users/a-bibeka/Dropbox/TTI_Projects/0-1-6934 TSC Settings Sunkari/Det_R_code/Through_Vid_STbar.pdf")

}
a
b
gResQ
gResQ1
gmax1a
gmax2a
AvgGr6
AvgGr4
graphics.off()
```
